---
title: "Lab 00 - Hello IDS!"
author: "Theo Sales"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Theo Sales", "Thomas Anderson", "Zach Zhao", 
           "Andrew Wraighd", "Daisy Luczaj", "Zaki Mulube"),
  github_username = c("andreww705", "zaki-mulube", "salestheo", 
                      "555bighandsome", "thomasBAnderson", "daisyluczaj"), 
  colour = c("red", "turquoise", "orange", 
             "pink", "darkgreen", "firebrick"),
  hobby = c("climbing", "kayaking", "reading", 
            "rugby", "basketball", "music"),
  favourite_number = c(7, 3, 3, 64, 7, 8)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


the plot shows our team's favorite number, scaled by size of that number and given in their favorite colour. 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "teammate", 
          y = "number",
          title = "team's favorite number")
```

labs () will change the axis labels for the plot

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

a better way of representing this data would be a picturegram of variable size representing the number of relevent entries for that hobby. 
